|

### 2021-08-07 prova_knit_finale.Rmd
knit e risolto bug seed

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  50
alpha =  0
beta  =  0.99
tau2  =  0.05
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]/2))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]/2))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2

@@

svpf<-SVPFfun(y,N,m0,C0, alpha,beta,tau)

svgpf<-SVGPFfun(y,N,m0,C0,alpha,beta,tau)

svapf<-SVAPFoptfun(y,N,m0,C0,alpha,beta,tau)

svlw<-SVLWfun(y,N,m0,C0,ealpha,valpha,ebeta,vbeta,nu,lambda)

@@

```{r echo=FALSE, fig.align='center', fig.cap="Comparison of filtering strategies for Stochastic Volatility Model. Filtered States with credible interval (in red)", fig.height=6, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}
plotone<-SVFiltplot(dfsv,svpf,"",3,-3)
plottwo<-SVFiltplot(dfsv,svgpf,"",3,-3)
plotthree<-SVFiltplot(dfsv,svapf,"",3,-3)
plotfour<-SVFiltplot(dfsv,svlw,"",3,-3)

@@

```{r include=FALSE}
set.seed(123)
truex<-x
estimatedx<-matrix(NA,ncol=5,nrow=4)
colnames(estimatedx)<-c("N","BPF","GPF", "APF","LWF")
estimatedx[,1]<-c(100,1000,10000,100000)

i=1
for(N in c(100,1000,10000,100000)){
set.seed(12345)

svpf_1<-SVPFfun(y,N,m0,C0, alpha,beta,tau)
svgpf_1<-SVGPFfun(y,N,m0,C0,alpha,beta,tau)
svapf_1<-SVAPFoptfun(y,N,m0,C0,alpha,beta,tau)
svlw_1<-SVLWfun(y,N,m0,C0,ealpha,valpha,ebeta,vbeta,nu,lambda)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
kbl(estimatedx, align="c", longtable = T, booktabs = T, caption="RMSE", digits=3)
```

>>>>

```{r include=FALSE}
# Simulating the data
# -------------------
set.seed(12345)
n     =  100
alpha =  0
beta  =  0.99
tau2  =  0.05
tau   = sqrt(tau2)
y     = rep(0,n)
x     = rep(0,n)
x[1]  = alpha/(1-beta)
y[1]  = rnorm(1,0,exp(x[1]/2))
for (t in 2:n){
  x[t] = alpha + beta*x[t-1] + rnorm(1,0,tau)
  y[t] = rnorm(1,0,exp(x[t]/2))
}
alpha.true = alpha
beta.true  = beta
tau2.true  = tau2

@@

set.seed(12345)
N1=N
svpf<-SVPFfun(y,N1,m0,C0, alpha,beta,tau)
set.seed(12345)
N1=N
svgpf<-SVGPFfun(y,N1,m0,C0,alpha,beta,tau)
set.seed(12345)
N1=N
svapf<-SVAPFoptfun(y,N1,m0,C0,alpha,beta,tau)
set.seed(12345)
N1=N
svlw<-SVLWfun(y,N1,m0,C0,ealpha,valpha,ebeta,vbeta,nu,lambda)

@@

```{r echo=FALSE, fig.align='center', fig.cap="Comparison of filtering strategies for Stochastic Volatility Model. Filtered States with credible interval (in red)", fig.height=6, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}
plotone<-SVFiltplot(dfsv,svpf,"",5,-5)
plottwo<-SVFiltplot(dfsv,svgpf,"",5,-5)
plotthree<-SVFiltplot(dfsv,svapf,"",5,-5)
plotfour<-SVFiltplot(dfsv,svlw,"",5,-5)

@@

```{r include=FALSE}
truex<-x
estimatedx<-matrix(NA,ncol=5,nrow=5)
colnames(estimatedx)<-c("N","BPF","GPF", "APF","LWF")
estimatedx[,1]<-c(20,100,1000,10000,100000)

i=1
for(N in c(20,100,1000,10000,100000)){

set.seed(12345)
N1=N
svpf_1<-SVPFfun(y,N1,m0,C0, alpha,beta,tau)
set.seed(12345)
N1=N
svgpf_1<-SVGPFfun(y,N1,m0,C0,alpha,beta,tau)
set.seed(12345)
N1=N
svapf_1<-SVAPFoptfun(y,N1,m0,C0,alpha,beta,tau)
set.seed(12345)
N1=N
svlw_1<-SVLWfun(y,N1,m0,C0,ealpha,valpha,ebeta,vbeta,nu,lambda)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
kbl(estimatedx, align="c", longtable = T, booktabs = T, caption="RMSE", digits=6)
```
